---
title: "Statistics Inference Assignment - 2"
author: "Liu Lee"
date: "24/10/2014"
output:
  html_document:
    highlight: zenburn
    theme: cosmo
  pdf_document:
    highlight: zenburn
    toc: yes
  word_document: default
---
  
***Details : This PDF contains solution and graph required to answer questions for assignment 2***

### Problem Statement - Statistics Inference 2

Now in the second portion of the class, we're going to analyze the ToothGrowth data in the R datasets package. 
1. Load the ToothGrowth data and perform some basic exploratory data analyses 

2. Provide a basic summary of the data.

3. Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose. (Use the techniques from class even if there's other approaches worth considering)

4. State your conclusions and the assumptions needed for your conclusions.

### Load Data 

```{r}
data(ToothGrowth)
head(ToothGrowth)
```

### Solution for Q1
```{r}
require(ggplot2)
g1 <- ggplot(ToothGrowth, aes(x = factor(dose), y = len,fill = factor(dose)))
g1 + geom_boxplot() + facet_grid(.~supp) + 
    scale_x_discrete("Dosage in mg") + 
    scale_y_continuous("Length of Teeth") + 
    ggtitle("Exploratory Data Analysis")

```

### Solution for Q2 
Basic summary of the data.

```{r}
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
summary(ToothGrowth)
table(ToothGrowth$supp, ToothGrowth$dose)
```

### Solution for Q3
We perform Null Hypothesis Test
```{r}
supp.t1 <- t.test(len ~ supp, paired = F, var.equal = T, data = ToothGrowth)
supp.t2 <- t.test(len~supp, paired = F, var.equal = F, data = ToothGrowth)
supp.result <- data.frame("p-value" = c(supp.t1$p.value, supp.t2$p.value),"Conf-Low" = c(supp.t1$conf[1],supp.t2$conf[1]),
                          "Conf-High" = c(supp.t1$conf[2],supp.t2$conf[2]), row.names = c("Equal Var","Unequal Var"))
supp.result
```

p-values for both equal and unequal variance t test > 5%. We can neither accept nor reject the Null hypothesis. So it is not clear that the difference exists between OJ and VC groups.

```{r}
dose.05 <- ToothGrowth[which(ToothGrowth$dose == .5),1]
dose.10 <- ToothGrowth[which(ToothGrowth$dose == 1),1]
dose.20 <- ToothGrowth[which(ToothGrowth$dose == 2),1]
dose0510.t1 <- t.test(dose.05, dose.10, paired = F, var.equal = T)
dose0510.t2 <- t.test(dose.05, dose.10, paired = F, var.equal = F)
dose0510.result <- data.frame("p-value" = c(dose0510.t1$p.value, dose0510.t2$p.value),"Conf-Low" = c(dose0510.t1$conf[1],dose0510.t2$conf[1]),"Conf-High" = c(dose0510.t1$conf[2],dose0510.t2$conf[2]), row.names = c("Equal Var","Unequal Var"), "Dose" = "0.5 to 1")
dose0520.t1 <- t.test(dose.05, dose.20, paired = F, var.equal = T)
dose0520.t2 <- t.test(dose.05, dose.20, paired = F, var.equal = F)
dose0520.result <- data.frame("p-value" = c(dose0520.t1$p.value, dose0520.t2$p.value),"Conf-Low" = c(dose0520.t1$conf[1],dose0520.t2$conf[1]),"Conf-High" = c(dose0520.t1$conf[2],dose0520.t2$conf[2]), row.names = c("Equal Var","Unequal Var"), "Dose" = "0.5 to 2")
dose1020.t1 <- t.test(dose.10, dose.20, paired = F, var.equal = T)
dose1020.t2 <- t.test(dose.10, dose.20, paired = F, var.equal = F)
dose1020.result <- data.frame("p-value" = c(dose1020.t1$p.value, dose1020.t2$p.value),"Conf-Low" = c(dose1020.t1$conf[1],dose1020.t2$conf[1]),"Conf-High" = c(dose1020.t1$conf[2],dose1020.t2$conf[2]), row.names = c("Equal Var","Unequal Var"), "Dose" = "1 to 2")
dose.result <- rbind(dose0510.result,dose0520.result,dose1020.result)
dose.result
```
Above table shows that dosages significantly impacts tooth growth. 

1. p-values are very small.

2. Confidence interval donot contain 0

So, we can reject the null hypothesis and state that higher dosage tends to result in higher tooth length


### Solution Q4

> We can conclude that across supplements for each dose :  
1. 2mg dose has larger impact on tooth growth than 1mg and 0.5mg  
2. 1mg dose has more impact than 0.5mg dose.   
3. we cannot say that orange juice and vitamin C have obvious different impact on tooth growth
